Adopting agile in the large: motivations, success factors and challenges

### 2014-01-13 journal/article.tex
Exclusion examples

Examples on topics excluded by the first facet are agile manufacturing, and
applying Scrum practices in management boards. In addition, we required that the
transformation was aimed to introduce agile methods into the studied
organization.

The facet of \emph{organizational transformation} was interpreted so that the
primary study presents insights on the process of transformation. Excluded
topics were: discussing a large agile effort but not presenting the how the
organization had evolved [ref?], pilot cases that clearly span one limited
project [Scott 2008?], and case studies that provide minimal information on the
transformation process [ref?].
--> Transformation and ``scaling up'' are very closely related. In some cases
    they can not really be separated. For instance, if transformation begins
    with a pilot and spreads gradually through the organization, it is very
    likely that the process is seen as a ``scaling up'' journey.
    However, in general, we do not include discussions purely on scaling up,
    especially if no organizational change is considered. [Maranzato 2012, Lyon 2008]

@@

@@

@@

\bibliography{sources_background}

>>>>

Examples on topics excluded by the first facet are agile manufacturing, and
applying Scrum practices in management boards, as these do not relate to
software engineering. In addition, we required that the organizational
transformation was aimed to introduce agile methods, which excluded other
development methods than agile (e.g. [Sagesser 2013]), and general talk on
organizational transformation.

The facet of \emph{organizational transformation} was interpreted so that the
primary study must present insights on the process of transformation. Some
topics that could clearly be excluded were discussing a large agile effort but

-- not presenting the how the organization had evolved [Fitzgerald?],
   Lyon [Lyon 2008] was excluded as it discusses technical challenges in scaling
   up an agile process instead of providing organizational viewpoints.

-- pilot cases that clearly span one limited project [Scott 2008?, Mc Cormic 2005],

-- a single team in a large organization [Fulgham, Jensen].

-- Some case studies that provide minimal information on the transformation process [Greening?].
   [Mishra 2011] discusses agile practices in a large organization, but does not
   provide viewpoints on the transformation process and introduction of agile methods.
   Kim [Kim 2012] sounds promising at a start, but merely presents agile tools
   lacking any transformation description.
   Also [Hodgkins].

Transformation and ``scaling up'' are very closely related and in some cases
they are one and the same. For instance, if transformation begins with a pilot
and spreads gradually through the organization, the process can very well be
seen as a ``scaling up'' journey. However, we did not include discussions purely
on scaling up, especially if no organizational change was considered. [Maranzato
2012, Lyon 2008]

@@

--> The case of difficult decision regarding size [Cloke 2007, Miller 2012].
--> [Tudor 2006] Exclude, borderline. There is no evidence on size. Many teams
    are mentioned, but there is still no direct indication of large size.

--> ``The team'' referring to a large organization [Hodgkins]

@@

It was quite common that a single transformation case was described by many
papers. For example, one paper would highlight the viewpoint of developers
\cite{Fry2007}, and another would consider the transformation from user
experience designers' point of view \cite{Federoff2009}. Instead of using the
most complete paper as suggested by Kitchenham \cite{Kitchenham2007}, we
combined the results presented in each paper and considered the case as a single
unit. By doing this we avoided bias caused by duplicate publications, and were
enabled to have a more detailed view of the case organization.

@@

\bibliography{sources_background,sources_primary}
